### 2021-12-20 thesis/tex/SM.tex
update

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{figures/SM_figure.pdf}
\end{figure}
\section{The Standard Model}\label{ch:SM}
In order to describe the three quantizable forces of nature, we gather the mediators of each force -- the vector bosons -- into local (gauge) symmetry groups. 
Each vector boson has one corresponding generator, the set of which constitutes the group.
The strong charge is mediated by eight massless gluons, which correspond to the eight independent generators of $\text{SU}(3)_C$. 
The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$, and the massless photon $\gamma$, 
which constitute the generators of $\text{SU}(2)_L$ and $\text{U}(1)_Y$.

@@

\section{Mass Generation}
In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
All neutrinos are left-handed, and all antineutrinos are right-handed~\cite{giunti}. This observational fact is reflected in the 
left-handed lepton doublet and right-handed lepton singlet

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{figures/SM_figure.pdf}
\end{figure}
\section{The Standard Model. Figure adapted from a diagram made by Carsten Burgard.}\label{ch:SM}
In order to describe the three quantizable forces of nature, we gather the mediators of each force -- the vector bosons -- into local (gauge) symmetry groups. 
Each vector boson has one corresponding generator, the set of which constitutes the group.
The strong charge is mediated by eight massless gluons, which correspond to the eight independent generators of $\text{SU}(3)_C$. 
The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$, and the massless photon $\gamma$, 
which constitute the generators of $\text{SU}(2)_L$ and $\text{U}(1)_Y$.

@@

\section{Mass Generation}
In the following sections, the presentation is following the outline in~\cite{giunti}.
In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
All neutrinos are left-handed, and all antineutrinos are right-handed~\cite{giunti}. This observational fact is reflected in the 
left-handed lepton doublet and right-handed lepton singlet
